Cover Letter

### 2023-10-22 manuscript/manuscript.qmd
Update

Asmaa Fahmy Kasem^1^, Hamdy Bakry Alqenawy^1^ ^\*^, Marwa Abd Elmawla Elgendi^1^, Radwa Rasheedy^1^, Rania Gamal^1^, Yasser M. Elrefaey^1^, Rowyna Hany Mohamed El Helw^1^, Rania Hassan Mostafa Ahmed^1^, Mohammad Nahel Sorour^1^, Mohamed Sameh Elsewefy^1^, Maya M. Abdelrazek^1^, Mohamed Yasser Galal Albahaie^1^, Khadiga Mostafa Hussein Hegab^1^, Mohamed H Salama^1^, Ashraf Nabhan^1^

@@

AN conceived the idea for this review and designed the review methods. xx, xx, xx collaborated in searching, screening, selecting studies, data extraction and synthesis. AN wrote the first draft of the manuscript and xx, xx, xx, xx, reviewed the manuscript. All authors read and approved the final version of the manuscript.

>>>>

Asmaa Fahmy Kasem^1^, Hamdy Bakry Alqenawy^1^ ^\*^, Marwa Abd Elmawla Elgendi^1^, Radwa Rasheedy^1^, Rania Gamal^1^, Yasser M. Elrefaey^1^, Rowyna Hany Mohamed El Helw^1^, Rania Hassan Mostafa Ahmed^1^, Mohammad Nahel Sorour^1^, Mohamed Sameh Elsewefy^1^, Maya M. Abdelrazek^1^, Mohamed Yasser Galal Albahaie^1^, Khadiga Mostafa Hussein Hegab^1^, Mohamed Hamed Salama^1^, Ashraf Fawzy Nabhan^1^

@@

AN conceived the idea for this review and designed the review methods. AFK, HBA coordinated the research activities. All authors collaborated in searching, screening, selecting studies, data extraction and synthesis. AFN, AFK, HBA wrote the first draft of the manuscript. All authors revised the manuscript critically for important intellectual content. All authors approved the final version of the manuscript. AFN is the guarantor for this manuscript.
